% LaTeX resume using res.cls
\documentclass[margin]{res}

% set up fonts
\usepackage[LGR,T1]{fontenc}
\usepackage{helvetica}
% \usepackage{tgheros} % if helvetica.sty is not available
\usepackage{tgpagella}
\usepackage{pifont}

\usepackage{setspace}

\setlength{\textwidth}{5.1in} % set width of text portion

% this value may need to be adjusted as content is added or removed.
\setlength{\parskip}{8pt}


% DRY
\newcommand{\widerule}{\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.1pt}}
\renewcommand{\labelitemi}{\ding{71}}

\begin{document}
\small
% Name and subtitle, left-aligned
\moveleft\hoffset\vbox{
	\LARGE
		\textbf{\textsf{Phillip T. Ridlen}}
		\textrm{ \{\textit{Web \& Software Developer}\}}
	}\bigskip\smallskip %\bigskip wasn't quite enough

% Contact information box
 \widerule\bigskip
 \moveleft1.06\hoffset\vbox{

  \begin{tabular}{l@{\hspace{.70in}}l@{\hspace{.5in}}|@{\hspace{.3in}}l@{\hspace{.70in}}l}
	  \textbf{\textsf{Address:}} & 2340 Trail Tree Ct  & \textbf{\textsf{Telephone:}}		& +1 682 233 3232               \\
                      & Burleson, TX 76028  & \textbf{\textsf{E-mail:}}			& phillip@ridlen.net            \\
                      & USA                 & \textbf{\textsf{Website:}}			& http://www.phillipridlen.com  \\
                      &                     &												& http://github.com/philtr	
  \end{tabular}}  
  \bigskip\widerule 

\begin{resume}\setstretch{1}

\section{\textsf{Skills}}

                \textit{General:} Attention to detail, Fast learner, Good listener, Effective communicator  \\
                \textit{Tools:} Ruby/Rails, PHP, MySQL, jQuery, Java, Git/Subversion, others                \\
                \textit{Design:} Photoshop, Illustrator, (X)HTML/CSS                                       %\\
                % \textit{Miscellaneous:} Microsoft Office, Apple iWork, \LaTeX

\vspace{10pt}

\section{\textsf{Education}}

                \textit{Bachelor of Science} in Software Engineering \dotfill May 2010   \\
								Minor in Mathematics \hfill  \textsc{The University of Texas at Arlington}                                                                
								                
                \textit{Certificate} in Biblical Studies \dotfill 2006  \\
                Emphasis in Computer Information Systems \hfill  \textsc{Emmaus Bible College}                    

\vspace{10pt}


\section{\textsf{Relevant \\ Experience}} 

                \textit{Interactive Developer}
				 at \textsc{Balcom Agency} in Fort Worth, TX\dotfill 2010--Present
				 \vspace{-10pt}\begin{itemize} \itemsep -2pt %reduce space between items
				 	\item Going to do some cool stuff!
				 \end{itemize}

                \textit{Web Guru}
                 at \textsc{Diverse Suspension Technologies} in Burleson, TX\dotfill 2009--2010
                 \vspace{-10pt}\begin{itemize} \itemsep -2pt %reduce space between items
                   \item Refreshed design of existing websites
                   \item Ensured XHTML compliance
                   \item Wrote a time clock application using Ruby on Rails
                \end{itemize}
                
                \textit{Freelance Web Development \textrm{\&} Graphic Design}
                in Burleson, TX\dotfill 2003--2010
                \vspace{-10pt}\begin{itemize} \itemsep -2pt %reduce space between items
                  \item Developed custom websites and WordPress themes
                  \item Designed print products for local bands, organizations, and businesses
                \end{itemize}
                
                \textit{OnForce Technician}
                at \textsc{Ball Corporation} in Fort Worth, TX\dotfill 2007--2009
                \vspace{-10pt}\begin{itemize} \itemsep -2pt %reduce space between items
                  \item Provided effective PC troubleshooting
                  \item Performed routine preventative maintenance on office desktop PCs
                \end{itemize}

\vspace{10pt}

      
\section{\textsf{Endorsements}}

                ``I can and do fully recommend Phillip for any position that requires 
                knowledge of standards--compliant HTML. There was no need for him to refresh his 
                memory on the subject and he flew through the work we asked of him.''             \\
                \textit{-- Graham Slaughter,} Owner of \textsc{Diverse Suspension Technologies}

                ``Phillip is someone who carefully reads the customer and then 
                provides the expected service. Phillip is truly a man of great character. 
                He puts his heart into anything he does. He doesn't hesitate to seek advice 
                to improve himself and his approach to a service or product.''                    \\
                \textit{-- Gibby Espinoza,} Customer

\vspace{10pt}
                

% Probably not going to need this section anymore
\section{\textsf{Honors \\and Awards}}
                
                \textit{Honor Roll,} University of Texas at Arlington. Spring/Fall 2009, Spring 2010 \\
                \textit{Dean's List,} Tarrant County College. Spring/Summer 2006

\vspace{12pt}


\textsf{\textbf{\footnotesize Contact information for personal and professional references is available upon request.}}

                
\end{resume}
\end{document}